### 2020-08-14 _meta/templates/Materials_and_methods__Data_preparation.Rmd
refactor

<EN>
The data show the variables in the columns and samples in the rows. However it was found that some samples are identical in proportions of ingredients, changing only the value of age and compressive strngth, for example, samples 653, 654, 678 and 681, shown in the table \ref{tab:similar-samples}.
</EN>

@@

```{r similar-samples, echo=FALSE}
#<EN># Tabela - Samples with same composition</EN>
#<PT># Tabela - Amostras com a mesma composição</PT>

@@

```{r similar-samples-2, echo=FALSE}
#<EN># Tabela - Same samples with different results</EN>
#<PT># Tabela - Amostras iguais com resultados diferentes</PT>

@@

```{r similar-samples-same-id, echo=FALSE, include=TRUE}
#<EN># Tabela - Previous samples after processing</EN>
#<PT># Tabela - Amostras anteriores após processamento</PT>

@@

As previously described, the main age for analysis of compressive strength is 28 days, but other ages can also be used to build forecasting models. However, it is necessary to verify how relevant the data of these other ages are. Starting with the distribution of the samples in relation to each age  (\ref{show-boxplot}) shown in the figure \ref{fig:boxplot}.
</EN>

@@

This hypothesis was verified using the principal component analysis method, applied to samples of these 3 ages (\ref{show-pca-90-91-100}). The figure \ref{fig:pca-90-91-100} shows how the samples relate to each other (which are similar or different) and revealed how each variable contributes to the analysis. The first two dimensions represent $ 37 \% $ and $ 24 \% $ respectively of the variance.
</EN>

@@

Essa hipótese foi verificada utilizando o método de análise de componente principal, aplicado às amostras dessas 3 idades (\ref{show-pca-90-91-100}). A fígura \ref{fig:pca-90-91-100} mostra como as amostras se relacionam umas com as outras (quais são parecidas ou diferentes) e revelou como cada variável contribui para a análise. As duas primeiras dimensões representam $37\%$ e $24\%$ respectivamente da variância.
</PT>

@@

<EN>
Another important point considered, of the concrete nature itself, is the fact that the growth rate of its compressive strength decreases with time, reaching a certain stability value. The figure \ref{fig:mpa-on-time} shows the compressive strength over the days for samples with more than 5 data, that is, data available for at least 6 different ages (\ref{show-mpa-on-team}).
</EN>

@@

<EN>
For the reasons presented in the figures \ref{fig:boxplot}, \ref{fig:pca-90-91-100} and \ref{fig:mpa-on-time}, it was considered that the ages of 90, 91 and 100 days can be grouped to improve reading and decrease sample noise. They were converted to the same value, the age of 100 days was chosen (\ref{show-join-90-91-100}. As shown in the figure \ref{fig:mpa-on-time}, the resistance only increases, after 100 days the resistance to compression will be greater than or equal to the value of 90 or 91 days.
</EN>

<PT>
Pelos motivos apresentados nas figuras \ref{fig:boxplot}, \ref{fig:pca-90-91-100} e \ref{fig:mpa-on-time}, foi considerado que as idades de 90, 91 e 100 dias podem ser agrupadas para melhorar a leitura e diminuir o ruído das amostras. Elas foram convertidas para o mesmo valor, que no caso foi escolhido a idade de 100 dias (\ref{show-join-90-91-100}, pois como mostrado na figura \ref{fig:mpa-on-time}, a resistência apenas aumenta, logo aos 100 dias a resistência à compressão será maior ou igual ao valor de 90 ou 91 dias.
</PT>

@@

The samples were grouped to maintain only a separate sample from each set of configuration of the proportions of the ingredients, adding new variables/columns for resistance at each age (\ref{show-reorganizing-dat}). The result in the first samples after this processing is shown in the table \ref{tab:new-features}.
</EN>

@@

To finish the data preparation, new columns were added to the dataset (\ref{show-new-features-2}). Starting with the concrete class, for example if the compressive strength is between 25 and 30, it receives the class *C25*. The inclusion of the class was important because the compressive strength in *MPa* is a continuous variable, which will be used in the regression models, but the class as a discrete variable can provide another visualization of the data. The approximate mix of concrete was also added, which represents the proportions of aggregates (fine and coarse) for cement. Other proportions between the main ingredients were also added. The new variables are presented in the table ref{tab:new-features-table}.
</EN>

>>>>

<EN>
The data show the variables in the columns and samples in the rows. However it was found that some samples are identical in proportions of ingredients, changing only the value of age and compressive strength, for example, samples 653, 654, 678 and 681, shown in the table \ref{tab:similar-samples}.
</EN>

@@

```{r similar-samples, echo=FALSE}
#<EN># Table - Samples with same composition</EN>
#<PT># Tabela - Amostras com a mesma composição</PT>

@@

```{r similar-samples-2, echo=FALSE}
#<EN># Table - Same samples with different results</EN>
#<PT># Tabela - Amostras iguais com resultados diferentes</PT>

@@

```{r similar-samples-same-id, echo=FALSE, include=TRUE}
#<EN># Table - Previous samples after processing</EN>
#<PT># Tabela - Amostras anteriores após processamento</PT>

@@

As previously described, the main age for analysis of compressive strength is 28 days, but other ages can also be used to build predictive models. However, it is necessary to verify how relevant the data of these other ages are. Starting with the distribution of the samples in relation to each age  (\ref{show-boxplot}) shown in the figure \ref{fig:boxplot}.
</EN>

@@

This hypothesis was verified using the principal component analysis method, applied to samples of these 3 ages (\ref{show-pca-90-91-100}). The figure \ref{fig:pca-90-91-100} shows how the samples relate to each other (which are similar or different) and revealed how each variable contributes to the analysis. The first two dimensions represent 37% and 24% $ respectively of the variance.
</EN>

@@

Essa hipótese foi verificada utilizando o método de análise de componente principal, aplicado às amostras dessas 3 idades (\ref{show-pca-90-91-100}). A fígura \ref{fig:pca-90-91-100} mostra como as amostras se relacionam umas com as outras (quais são parecidas ou diferentes) e revelou como cada variável contribui para a análise. As duas primeiras dimensões representam 37% e 24% respectivamente da variância.
</PT>

@@

<EN>
Another important point considered, of the concrete nature itself, is the fact that the growth rate of its compressive strength decreases with time, reaching a certain stability value. The figure \ref{fig:mpa-on-time} shows the compressive strength over the days for samples with more than 5 data, that is, data available for at least 6 different ages (\ref{show-mpa-on-time}).
</EN>

@@

<EN>
For the reasons presented in the figures \ref{fig:boxplot}, \ref{fig:pca-90-91-100} and \ref{fig:mpa-on-time}, it was considered that the ages of 90, 91 and 100 days can be grouped to improve reading and decrease sample noise. They were converted to the same value, the age of 100 days was chosen (\ref{show-join-90-91-100}). As shown in the figure \ref{fig:mpa-on-time}, the resistance only increases, after 100 days the resistance to compression will be greater than or equal to the value of 90 or 91 days.
</EN>

<PT>
Pelos motivos apresentados nas figuras \ref{fig:boxplot}, \ref{fig:pca-90-91-100} e \ref{fig:mpa-on-time}, foi considerado que as idades de 90, 91 e 100 dias podem ser agrupadas para melhorar a leitura e diminuir o ruído das amostras. Elas foram convertidas para o mesmo valor, que no caso foi escolhido a idade de 100 dias (\ref{show-join-90-91-100}), pois como mostrado na figura \ref{fig:mpa-on-time}, a resistência apenas aumenta, logo aos 100 dias a resistência à compressão será maior ou igual ao valor de 90 ou 91 dias.
</PT>

@@

The samples were grouped to maintain only one sample from each set of configuration of the proportions of the ingredients, adding new variables/columns for resistance at each age (\ref{show-reorganizing-dat}). The result in the first samples after this processing is shown in the table \ref{tab:new-features}.
</EN>

@@

To finish the data preparation, new columns were added to the dataset (\ref{show-new-features-2}). Starting with the concrete class, for example if the compressive strength is between 25 and 30, it receives the class *C25*. The inclusion of the class was important because the compressive strength in *MPa* is a continuous variable, which will be used in the regression models, but the class as a discrete variable can provide another visualization of the data. The approximate mix of concrete was also added, which represents the proportions of aggregates (fine and coarse) for cement. Other proportions between the main ingredients were also added. The new variables are presented in the table \ref{tab:new-features-table}.
</EN>

### 2020-08-14 _meta/templates/Materials_and_methods__Machine_learning_models.Rmd
refactor

The development of machine learning models was carried out with the *caret* package [@caret] and based on @irizarry2019 e @Kuhn2008.

@@

Como existe a variável categórica para o traço aproximado do concreto, foi realizada a conversão dessa variável em variáveis fictiícias (*dummy vars*) (\ref{show-dummy-var}), passando de 22 colunas (id, classe, resistência à compressão e mais 19 *features*) para 45 colunas, uma adição de 23 variáveis, uma para cada traço aproximado.

@@

<EN>
The samples were separated based on age. One dataset was created for each age value, totaling 6 different sets (\ref{show-preparation}). For illustrative purposes, the first 18 of 45 columns of the first 6 samples from the 28-day set are shown in the table \ref{tab:table-prepared-samples}.
</EN>

@@

dat_tabela <- dat_28[1:18]

kable(
    head(dat_tabela[order(dat_tabela$id),]),
    col.names = dfUnits,
    escape = F,
    booktabs = T,
    caption = caption,
    linesep = "\\addlinespace",
    digits = 2,
    align = "c"
    ) %>%
    add_header_above(header = colNames, line = F, align = "c") %>%
    kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

@@

As new variables were added throughout the processing (the relationships between the ingredients and a few more *dummy vars* for each age set), 5 possibilities for configuring the *features* for the models were studied:

1. All *features*;
2. All *features* without the *dummy vars*;
3. Only the original *features*;
4. Only new *features*;
5. Only new *features*, without *dummy vars*;

Building a model for each of these configurations using the set at 28 days (\ref{show-test-models-reg}), showed that the best option is configuration 2, the *dummy vars* were completely discarded, but the other new variables were kept.

For illustrative purposes, the \ref{tab:table-done-samples-28} table shows the first 6 samples from the 28-day model training set. The samples of the other models, of the test and training sets are similar, the only difference being in the 7-day model, which excludes fly ash due to the variance close to zero, performed previously.
</EN>

@@

Como ao longo do processamento foram adicionadas novas variáveis (as relações entre os ingredientes e mais algumas *dummy vars* para cada conjunto de idade), foram estudadas 5 possibilidades de configurações das *features* para os modelos:

1. Todas as *features*;
2. Sem as *dummy vars*;
3. Apenas *features* originais;
4. Apenas *features* adicionadas;
5. Apenas *features* adicionadas, sem as *dummy vars*;

Construindo um modelo para cada uma dessas configurações utilizando o conjunto de amostras aos 28 dias (\ref{show-test-models-reg}), mostrou que a melhor opção é a configuração 2, ou seja, as *dummy vars* foram completamente descartadas, porém foram mantidas as outras novas varáveis.

>>>>

The development of machine learning models was carried out with the *caret* package [@caret] and based on @irizarry2019 and @Kuhn2008.

@@

@@

<EN>
The samples were separated based on age. One dataset was created for each age value, totaling 6 different sets (\ref{show-preparation}). For illustrative purposes, the first 18 of 45 columns of the first 6 samples from the 28-day set are shown in the table \ref{tab:table-preparated-samples}.
</EN>

@@

dat_table <- dat_28[1:18]

kable(
    head(dat_table[order(dat_table$id),]),
    col.names = dfUnits,
    escape = F,
    booktabs = T,
    caption = caption,
    linesep = "\\addlinespace",
    digits = 2,
    align = "c"
    ) %>%
    add_header_above(header = colNames, line = F, align = "c") %>%
    kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

@@

As new variables were added throughout the processing (the relationships between the ingredients and a few more *dummy vars* for each age set), 5 possibilities for configuring the *features* for the models were studied:
&nbsp;
1. All *features*;
2. All *features* without the *dummy vars*;
3. Only the original *features*;
4. Only new *features*;
5. Only new *features*, without *dummy vars*;
&nbsp;
Building a model for each of these configurations using the set at 28 days (\ref{show-test-models-reg}), showed that the best option is configuration 2, the *dummy vars* were completely discarded, but the other new variables were kept.

For illustrative purposes, the table \ref{tab:table-done-samples-28} shows the first 6 samples from the 28-day model training set. The samples of the other models, of the test and training sets are similar, the only difference being in the 7-day model, which excludes fly ash due to the variance close to zero, performed previously.
</EN>

@@

Como ao longo do processamento foram adicionadas novas variáveis (as relações entre os ingredientes e mais algumas *dummy vars* para cada conjunto de idade), foram estudadas 5 possibilidades de configurações das *features* para os modelos:
&nbsp;
1. Todas as *features*;
2. Sem as *dummy vars*;
3. Apenas *features* originais;
4. Apenas *features* adicionadas;
5. Apenas *features* adicionadas, sem as *dummy vars*;
&nbsp;
Construindo um modelo para cada uma dessas configurações utilizando o conjunto de amostras aos 28 dias (\ref{show-test-models-reg}), mostrou que a melhor opção é a configuração 2, ou seja, as *dummy vars* foram completamente descartadas, porém foram mantidas as outras novas varáveis.

### 2020-08-14 _meta/templates/Results.Rmd
refactor

<PT>
# Results

@@

```{r table-reg-models, echo=F}
#<EN># Table - Models details</EN>
#<PT># Tabela - Detalhes dos modelso</PT>

@@

res_df <- lapply(1:6, gen_res_df)
res_df <- bind_rows(res_df)
res_df$model <- factor(res_df$modelo,levels=modelos)

res_df %>%
  ggplot(aes(actual, pred)) +
  facet_wrap(~ modelo, ncol=3) +
  geom_point(alpha=0.5) +
  theme_bw() +
  geom_abline(slope=1, intercept=0) +
  xlab(xlabel) +
  ylab(ylabel)
```

>>>>

<PT>
# Resultados

@@

```{r table-reg-models, echo=F}
#<EN># Table - Models details</EN>
#<PT># Tabela - Detalhes dos modelos</PT>

@@

res_df <- lapply(1:6, gen_res_df)
res_df <- bind_rows(res_df)
res_df$model <- factor(res_df$model,levels=models)

res_df %>%
  ggplot(aes(actual, pred)) +
  facet_wrap(~ model, ncol=3) +
  geom_point(alpha=0.5) +
  theme_bw() +
  geom_abline(slope=1, intercept=0) +
  xlab(xlabel) +
  ylab(ylabel)
```
